OpenMPIR

### 2017-09-08 paper.tex
More updates.

To better understand how the OpenMP to Tapir compiler works, we turn to the
\texttt{fib} example from Section~\ref{Sec:OpenMP}. In \figref{tapir-example}
we show what Tapir code is generated.

@@

The listed Tapir LLVM IR code corresponds to lines 7 through 12 of the C source
code.  Upon entering the \texttt{else} branch, the code immediately detaches
the basic block corresponding to the call to \texttt{fib(n-1)}, labeled
\texttt{det.achd}. The continuation for the first call also immediately
detaches the basic block corresponding to the call of \texttt{fib(n-2)}.
Finally, the continuation for the second call immediately calls sync. This is
actually a nice example of code that will be optimized by Tapir. The LLVM code
shown in Figure~\ref{tapir-example} is not optimized. With optimizataions turned
on, Tapir will replace a \texttt{detach} of a function call followed
immediately by \texttt{sync} with a simple function call, resulting in faster
code.

@@

For evaluation we compared performance on the Barcelona OpenMP task suite
\cite{barcelona} to existing OpenMP implementations. The Barcelona OpenMP task
suite is a set of tests intended to test performance of OpenMP implementations
using both irregular and regular tasking. The benchmark suite has added an
unbalanced tree search benchmark since the paper was published. Unfortunately
we were unable to succesfully run it on any implementation, even for even
medium input sizes. We have therefore left it out of our evaluation. The
following descriptions are abridged versions taken verbatim from
\cite{barcelona}:

>>>>

To better understand how the OpenMP to Tapir compiler works, we turn to the
\texttt{fib} example from Section~\ref{Sec:OpenMP}. In \figref{tapir-example}
we show the input OpenMP program and a portion of the corresponding Tapir code 
that is generated.

@@

The listed Tapir IR code corresponds to lines 7 through 12 of the C source
code.  Upon entering the \texttt{else} branch, the code immediately detaches
the basic block corresponding to the call to \texttt{fib(n-1)}, labeled
\texttt{det.achd}. The continuation for the first call also immediately
detaches the basic block corresponding to the call of \texttt{fib(n-2)}.
Finally, the continuation for the second call immediately calls sync. This is
actually a nice example of code that will be optimized by Tapir. The LLVM code
shown in \figref{tapir-example} is not optimized. With optimizataions turned
on, Tapir will replace a \texttt{detach} of a function call followed
immediately by \texttt{sync} with a simple function call, resulting in faster
code.

@@

For evaluating the use of Tapir we compared performance on the Barcelona OpenMP Task 
Suite~\cite{barcelona} to several existing OpenMP implementations. The suite is a set 
of tests intended to test performance of OpenMP implementations
using both irregular and regular tasking.\footnote{An unbalanced tree search benchmark was
very recently added to the suite. Unfortunately we were unable to succesfully run 
it on any implementation, even for even medium input sizes. We have therefore left 
it out of our evaluation.  We will continue to work on this benchmark and will 
include the results if the paper is accepted to the workshop.} The following list provides abridged descriptions of 
each benchmark -- they are taken verbatim from~\cite{barcelona}:
